How has the Brazilian Amazon been constructed as a problem? The economy, the environment, the people, and the nation in the presidential speeches since 1985

### 2022-05-31 Draft_April_2022/Full_draft_20220401.rmd

```{r Figure 1: Amazonian speeches by year, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, include=TRUE}
perc1 <- pop %>%
  count(amazon_speech, year)%>%
  group_by(year)%>%
  mutate(perc=n / sum(n)) %>%
  select(c(perc,amazon_speech, year))
pop2 <- pop %>% count(amazon_speech, year, president) %>%
  group_by(year, president) %>%
  left_join(perc1) %>%
  filter(amazon_speech==1)
pop2 <- left_join(pop2, AAI, by = "year")
pop2 <- left_join(pop2, amazon_def_year, by = "year")
model <- lm(perc ~ AAI+ def_year + president, data=pop2)
pop2$predicted = predict(model, pop2)
Amazon_year <- pop2 %>% ggplot(., aes(x = year, y = perc)) +
  geom_line(size=.85, aes(x=year, y=perc, color="Real share")) +
  geom_line(size=.45, aes(x=year, y=predicted, color= "Predicted share")) +
  geom_text(aes(x = 1988, y = 0.34, label = "Chico Mendes/NYT"), size = 3) +
  geom_vline(xintercept = 1988, linetype="dotted") +
  geom_text(aes(x = 1992, y = 0.27, label = "Earth Summmit"), size = 3) + 
  geom_vline(xintercept = 1992, linetype="dotted") +
  geom_text(aes(x = 2009, y = 0.25, label = "Copenhagen Summmit"), size = 3) + 
  geom_vline(xintercept = 2009, linetype="dotted") +
  geom_text(aes(x = 2015, y = 0.21, label = "Paris Summmit"), size = 3) + 
  geom_vline(xintercept = 2015, linetype="dotted") +
  scale_color_manual(values = c("Real share" = "darkolivegreen", "Predicted share" = "gray40")) +
  scale_y_continuous(labels = percent_format()) +
  labs(x = "", y = "", title ="Share of speeches mentioning the Amazon by year",
       subtitle = "Sample composed by 6130 presidential speeches since 1985",
       caption = "Predicted share controls for deforestation rates, inflation, and president.",
       color='Y series') +
  theme(panel.background = element_rect("white", "black", .5, "solid"),
        panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
        axis.text = element_text(color = "black", size = 10),
        title = element_text(color = "black", size = 10, face = "bold"),
        legend.title = element_blank(),
        plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
        legend.position = "bottom")
Amazon_year
```

@@

```{r Figure 2: mixed-types in time, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
prob_construction_year <- ama_mx %>%
  filter(!(mx_cat == "Other" | mx_cat == "Other Mixed-types")) %>% 
  count(year, mx_cat) %>%
  group_by(year) %>%
  mutate(perc = n / sum(n)) %>% 
  ggplot(aes(x=year, y=perc, fill=mx_cat)) +
  geom_bar(stat="identity", position="dodge") +
  geom_smooth(color="black", size=.3, se= FALSE) +
  scale_y_continuous(labels = percent_format(accuracy=1)) +
  labs(x = "", y = "", title ="Share of different problem-constructions by year",
       subtitle = "Sample composed by 1895 Amazonian statements in presidential speeches since 1985", caption = "") +
  theme(panel.background = element_rect("white", "black", .5, "solid"),
        panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
        axis.text = element_text(color = "black", size = 10),
        title = element_text(color = "black", size = 10, face = "bold"),
        legend.title = element_blank(),
        plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
        legend.position = "none") +
  facet_wrap(~ mx_cat, ncol = 2)
prob_construction_year
```

@@

```{r Figure 3: pure types in time , echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
pure_types_time <- ama_mx %>%
  count(mx_cat, mx_cat2, year) %>%
  group_by(year) %>%
  mutate(perc = n / sum(n)) %>% 
  filter(mx_cat2 == "Pure-types") %>% 
  ggplot(aes(x=as.numeric(year), y = perc, color = mx_cat)) +
  geom_smooth(aes(fill = mx_cat), size = .5) +
  scale_y_continuous(labels = percent_format(accuracy = 1)) +
  labs(x = "", y = "", title ="Share of each pure type by year",
       subtitle = "Sample composed by 1895 Amazonian statements in presidential speeches since 1985",
       caption = "") +
  theme(panel.background = element_rect("white", "black", .5, "solid"),
        panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
        axis.text = element_text(color = "black", size = 10),
        title = element_text(color = "black", size = 10, face = "bold"),
        legend.title = element_blank(),
        plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
        legend.position = "bottom")
pure_types_time
```

@@

```{r Figure 5: pure types in time by location, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE, out.width= "50%"}
pure_types_time_location <- ama_mx %>%
  count(mx_cat2, mx_cat, year, location_cat) %>%
  group_by(year) %>%
  mutate(perc = n / sum(n)) %>% 
  filter(mx_cat2 == "Pure-types") %>%
  filter(location_cat != "Non Identified") %>%
  ggplot(aes(x=as.numeric(year), y=perc, color=mx_cat)) +
  geom_smooth(aes(color=mx_cat), se=FALSE, size=.5) +
  scale_y_continuous(labels = percent_format(accuracy=1)) +
  labs(x = "", y = "", title ="Share of each pure type in time by location",
       subtitle = "Sample composed by 1895 Amazonian statements in presidential speeches since 1985",
       caption = "") +
  theme(panel.background = element_rect("white", "black", .5, "solid"),
        panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
        axis.text = element_text(color = "black", size = 10),
        title = element_text(color = "black", size = 10, face = "bold"),
        legend.title = element_blank(),
        plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
        legend.position = "bottom") +
  facet_wrap(~location_cat, ncol=2)
pure_types_time_location
```

@@

```{r Figure 6: probability for constructions across locations, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
logit2prob <- function(logit) {
  odds <- exp(logit)
  prob <- odds / (1 + odds)
  return(prob)
}
md_plot <- data.frame("Construction" = c("Economic Integration", "Social Development", "Sovereignty"),
                      "Brasilia" = c(-1.024, -1.002, -0.206),
                      "International" = c(-0.612, -1.583, -1.427),
                      "Other_States" = c(0.023, -0.041, 0.324))
md_plot$Brasilia <- logit2prob(md_plot$Brasilia)
md_plot$International <- logit2prob(md_plot$International)
md_plot$Other_States <- logit2prob(md_plot$Other_States)
mplot <- md_plot %>%
  tidyr::pivot_longer(Brasilia:Other_States) %>%
  mutate(Probability = round(value, digit = 2)) %>% 
  rename(Location = name) %>% 
  ggplot(aes(Location, Probability, fill = Construction)) +
  geom_bar(stat = "identity", position = position_dodge(0.8), width = 0.7) +
  scale_fill_brewer(type = "qual", palette = "Set2", direction= 1) +
  geom_text(aes(label = Probability), vjust = 1.5, size = 3, position = position_dodge(0.8)) +
  geom_hline(yintercept = 0.5, linetype = "dotted", color = "red") +
  labs(x = "", y = "Probability",
       title = "Probability for problem constructions across locations",
       subtitle = "Reference category is environmental conservation problem-construction in Amazonian States") +
    theme(panel.background = element_rect("white", "black", .5, "solid"),
          panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
          axis.text = element_text(color = "black", size = 10),
          title = element_text(color = "black", size = 10, face = "bold"),
          legend.title = element_blank(),
          plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
          legend.position = "bottom")
mplot
```

>>>>

```{r Figure 1: Amazonian speeches by year, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, include=TRUE}
perc1 <- pop %>%
  count(amazon_speech, year)%>%
  group_by(year)%>%
  mutate(perc=n / sum(n)) %>%
  select(c(perc,amazon_speech, year))
pop2 <- pop %>% count(amazon_speech, year, president) %>%
  group_by(year, president) %>%
  left_join(perc1) %>%
  filter(amazon_speech==1)
pop2 <- left_join(pop2, AAI, by = "year")
pop2 <- left_join(pop2, amazon_def_year, by = "year")
model <- lm(perc ~ AAI+ def_year + president, data=pop2)
pop2$predicted = predict(model, pop2)
Amazon_year <- pop2 %>% ggplot(., aes(x = year, y = perc)) +
  geom_line(size=.85, aes(x=year, y=perc, color="Real share"))+
  geom_line(size=.45, aes(x=year, y=predicted, color= "Predicted share"))+
  scale_color_manual(values=c("Real share"="darkolivegreen", "Predicted share"= "gray40"))+
  scale_y_continuous(labels = percent_format())+
  labs(x = "", y = "", title ="Share of speeches mentioning the Amazon by year",
       subtitle = "Sample composed by 6130 presidential speeches since 1985",
       caption = "Predicted share controls for deforestation rates, inflation, and president.", color='Y series') +
  theme(panel.background = element_rect("white", "black", .5, "solid"),
        panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
        axis.text = element_text(color = "black", size = 10),
        title = element_text(color = "black", size = 10, face = "bold"),
        legend.title = element_blank(),
        plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
        legend.position = "bottom")
Amazon_year
```

@@

```{r Figure 2: mixed-types in time, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
prob_construction_year <- ama_mx %>%
  count(year, mx_cat)%>%
  group_by(year) %>%
  mutate(perc = n / sum(n)) %>%
  ggplot(aes(x=year, y=perc, fill=mx_cat)) +
  geom_bar(stat="identity", position="dodge") +
  geom_smooth(color="black", size=.3, se= FALSE) +
  scale_y_continuous(labels = percent_format(accuracy=1)) +
  labs(x = "", y = "", title ="Share of different problem-constructions by year",
       subtitle = "Sample composed by 1895 Amazonian statements in presidential speeches since 1985", caption = "") +
  theme(panel.background = element_rect("white", "black", .5, "solid"),
        panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
        axis.text = element_text(color = "black", size = 10),
        title = element_text(color = "black", size = 10, face = "bold"),
        legend.title = element_blank(),
        plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
        legend.position = "none") +
  facet_wrap(~ mx_cat, ncol=3, scales="free_y")
prob_construction_year
```

@@

```{r Figure 3: pure types in time , echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
pure_types_time <- ama_mx %>%
  count(president, mx_cat2, mx_cat, year) %>%
  group_by(president, year) %>%
  mutate(perc = n / sum(n)) %>% 
  filter(mx_cat2 == "Pure-types") %>% 
  ggplot(aes(x=as.numeric(year), y=perc, color=mx_cat)) +
  geom_smooth(aes(color=mx_cat), se=FALSE, size=.5) +
  scale_y_continuous(labels = percent_format(accuracy=1)) +
  labs(x = "", y = "", title ="Share of each pure type by year",
       subtitle = "Sample composed by 1895 Amazonian statements in presidential speeches since 1985",
       caption = "") +
  theme(panel.background = element_rect("white", "black", .5, "solid"),
        panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
        axis.text = element_text(color = "black", size = 10),
        title = element_text(color = "black", size = 10, face = "bold"),
        legend.title = element_blank(),
        plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
        legend.position = "bottom")
pure_types_time
```

@@

```{r Figure 5: pure types in time by location, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE, out.width= "50%"}
pure_types_time_location <- ama_mx %>%
  count(mx_cat2, mx_cat, year, location_cat) %>%
  group_by(year) %>%
  mutate(perc = n / sum(n)) %>% 
  filter(mx_cat2 == "Pure-types") %>%
  filter(location_cat != "Non Identified") %>%
  ggplot(aes(x=as.numeric(year), y=perc, color=mx_cat)) +
  geom_smooth(aes(color=mx_cat), se=FALSE, size=.5) +
  scale_y_continuous(labels = percent_format(accuracy=1)) +
  labs(x = "", y = "", title ="Share of each pure type in time by location",
       subtitle = "Sample composed by 1895 Amazonian statements in presidential speeches since 1985",
       caption = "") +
  theme(panel.background = element_rect("white", "black", .5, "solid"),
        panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
        axis.text = element_text(color = "black", size = 10),
        title = element_text(color = "black", size = 10, face = "bold"),
        legend.title = element_blank(),
        plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
        legend.position = "bottom") +
  facet_wrap(~location_cat, scales= "free_y", ncol=2)
pure_types_time_location
```

@@

```{r Figure 6: probability for constructions across locations, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
logit2prob <- function(logit) {
  odds <- exp(logit)
  prob <- odds / (1 + odds)
  return(prob)
}
md_plot <- data.frame("Construction" = c("Economic Integration", "Social Development", "Sovereignty"),
                      "Brasilia" = c(-1.024, -1.002, -0.206),
                      "International" = c(-0.612, -1.583, -1.427),
                      "Other_States" = c(0.023, -0.041, 0.324))
md_plot$Brasilia <- logit2prob(md_plot$Brasilia)
md_plot$International <- logit2prob(md_plot$International)
md_plot$Other_States <- logit2prob(md_plot$Other_States)
mplot <- md_plot %>% tidyr::pivot_longer(Brasilia:Other_States) %>%
  rename(Location = name, Probability = value) %>% 
  ggplot(aes(Construction, Probability)) +
  geom_bar(aes(fill = Location), stat = "identity", position = position_dodge(0.8), width = 0.7) +
    scale_fill_brewer(type = "qual", palette = "Set2", direction= 1) +
  labs(x = "", y = "Probability",
       title = "Probability for problem constructions across locations",
       subtitle = "Reference category is environmental conservation problem-construction in Amazonian States") +
    theme(panel.background = element_rect("white", "black", .5, "solid"),
        panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
        axis.text = element_text(color = "black", size = 10),
        title = element_text(color = "black", size = 10, face = "bold"),
        legend.title = element_blank(),
        plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
        legend.position = "bottom")
mplot
```
